### 2020-09-01 thesis/thesis.tex
[thesis] Resolve pending TODOs with citations

It turns out, that it becomes complex and unpleasant to combine two functors
together to form a new monad, and for this purpose, monad
transformers~\cite{monad-transformers} arose in Haskell. Most of the common
languages avoid this by not expressing computational effects in the type system,
and instead one may think about functions as being implicitly embed in a Kleisli
Category over a functor $T$~\cite{kleisli-ncatlab}, where $T$ is a hidden signature
over all possible side effects that occur in our program.

% TODO Reconsider reference to ncatlab on Kleisli Cat, often it's not the best resource

@@

    From categorical standpoint, coinduction is formed over a final coalgebra,
    where corecursion is the mediator between any coalgebra into a final one,
    and coinductive proof principle corresponds to the uniqueness of the mediator.
    Recall from Chapter~\ref{chapter:background} that coalgebraic effects arises from cofree coalgebra.

    % TODO Not sure which paper to cite here for a deeper dive into the upper
    % topic. Book \textit{Initial Algebras, Terminal Coalgebras, and the Theory of Fixed Points of Functors}
    % by Adámek, Milius and S. Moss from which I have studied is no longer available
    % on the internet, as it was a draft under construction.

>>>>

It turns out, that it becomes complex and unpleasant to combine two functors
together to form a new monad, and for this purpose, monad
transformers~\cite{monad-transformers} arose in Haskell. Most of the common
languages avoid this by not expressing computational effects in the type system,
and instead one may think about functions as being implicitly embed in a Kleisli
Category over a functor $T$~\cite{kleisli}, where $T$ is a hidden signature
over all possible side effects that occur in our program.

@@

    From categorical standpoint, coinduction is formed over a final coalgebra,
    where corecursion is the mediator between any coalgebra into a final one,
    and coinductive proof principle corresponds to the uniqueness of the mediator.
    Recall from Chapter~\ref{chapter:background} that coalgebraic effects arises
    from cofree coalgebra. For more information about coalgebras, see~\cite{jacobs-2016}.
